```{r}
library(tidyverse)
```

## Reading the dataset into Rstudio ## 
```{r}

# importing the CSV file of the Data Entry into R as a data frame
df <- read.csv("CXT SURA Data Entry (Responses) - Form Responses 1.csv")

# shortening all the column names in the dataset
names(df) <- c("timestamp", "courseNum", "semester", "DCID", "assignmentTime", "assignmentType", "cxt1", "cxt1_Comments", "cxt2a", "cxt2a_Comments", "cxt2b", "cxt2b_Comments", "cxt3", "cxt3_Comments","cxt4a", "cxt4a_Comments","cxt4b", "cxt4b_Comments","overallComments", "Coder", "numPages")

# turning the course into a categorical variable
df$courseNum <- factor(df$courseNum)

```


## Modifying the dataset (adding new columns/variables) ##

```{r}
 df <- df %>% 
  # excluding the CXT comments columns and timestamp columns
  select(courseNum, semester, DCID, assignmentTime, 
          assignmentType, cxt1, cxt2a, cxt2b, cxt3, cxt4a, cxt4b, Coder, 
          numPages) %>%
  # adding a course discipline variable into the dataset
  mutate(
    
    # Social Science for 85-221: Pricinples of Child Development and 84-389: Terrorism and Insurgency
    # Humanities otherwise
    courseDiscipline = ifelse(
      courseNum %in% c("85221", "84389"), "Social Science", "Humanities")
    
    ) %>% 
  
  # grouping artifacts together by course number to add a new variable into each artifact
  group_by(courseNum) %>% 
  
  # adding a variable for whether the course assigned multiple types of assignments in the semester
  mutate(
    # More than 1 assignment type detected for a course = 1, 0 otherwise
    IsVaried = ifelse(n_distinct(assignmentType) > 1, 1, 0)
  ) %>% 
  
  # returning back into a normal dataframe with the new columns/variables added
  ungroup()
```


## Making a separate dataframe for each jointly coded course in the dataset ##
```{r}
# dataframe for Fall 2021 85-221 Principles of Child Development 
F21_85221 <- df %>%
  filter(courseNum == "85221") %>% 
  filter(semester == "F21")  %>% 
  # only considering the reconciled ratings of the artifacts to avoid duplicates
  filter(Coder == "Reconciled Code") 

# dataframe for Fall 2024 82-273 Japanese Culture and Society
F24_82273 <- df %>%
  filter(courseNum == "82273") %>% 
  filter(semester == "F24")  %>% 
  # only considering the reconciled ratings of the artifacts to avoid duplicates
  filter(Coder == "Reconciled Code")  

# dataframe for Spring 2025 84-389 Terrorism and Insurgency
S25_84389 <- df %>%
  filter(courseNum == "84389") %>% 
  filter(semester == "S25")  %>% 
  # only considering the reconciled ratings of the artifacts to avoid duplicates
  filter(Coder == "Reconciled Code")
  
```

## Making a separate dataframe for each non-jointly coded course in the dataset ##
```{r}
# dataframe for Spring 2022 82-273 Japanese Culture and Society
S22_82273 <- df %>%
  filter(courseNum == "82273") %>% 
  filter(semester == "S22")

# dataframe for Fall 2024 82-270 Technology in Japanese Culture and Society
F24_82270 <- df %>%
  filter(courseNum == "82270") %>% 
  filter(semester == "F24")

# dataset for Spring 2026 84-389 Terrorism and Insurgency
S26_84389 <- df %>%
  filter(courseNum == "84389") %>% 
  filter(semester == "S26")  

# dataset for Fall 2025 79-211 Modern Southeast Asia
F25_79211 <- df %>%
  filter(courseNum == "79211") %>% 
  filter(semester == "F25")

# dataset for Fall 2021 76-247 Shakespeare: Comedies & Romances
F21_76247 <- df %>%
  filter(courseNum == "76247") %>% 
  filter(semester == "F21")
```

## Modifying the Dataset ##
```{r}

# reading into R the student demographics dataset
demographics_df <- read.csv("Demographics_SURA.csv")

# creating the new modified dataset with only coded artifacts from non-business courses
# and student demographics 
modified_df <- F21_76247 %>% # combining all individual course datasets together
  bind_rows(F21_85221) %>% 
  bind_rows(F24_82270) %>%
  bind_rows(F24_82273) %>%
  bind_rows(F25_79211) %>%
  bind_rows(S22_82273) %>%
  bind_rows(S25_84389) %>%
  bind_rows(S26_84389) %>% 
  # adding demographics info for each unique DCID
  left_join(demographics_df, by = c("DCID" = "DCID2")) %>% 
  rowwise %>% 
  # creating an additional variable for specific courses and their semester
  # to avoid mix up
  mutate(
    semester_courseNum = paste0(semester, "_", courseNum)
  )
  
```

## Creating Binary Grid Plot of the Assignment Type Given by Each Course ##

```{r}

# dataframe for setting binary grid plot
course_assignment_binary <- modified_df %>%
  # keep only one artifact from each course and their assignment type
  distinct(semester_courseNum, assignmentType) %>% 
   # add a new variable that checks if there is an early and/or late assignment
  # assigned by a course
  mutate(Assigned = TRUE) %>% 
  # turns the missing values of assignment time into FALSE for the assigned variable
  complete(semester_courseNum, assignmentType = c("Short Paper", "Reflection", "Final Paper"), fill = list(Assigned = FALSE))

ggplot(course_assignment_binary, aes(x = assignmentType, y = semester_courseNum, fill = Assigned)) +
  # tile plot
  geom_tile(color = "black", lwd = 1) + 
  
  # color specification
  scale_fill_manual(
    values = c("TRUE" = "green", "FALSE" = "red"), # Pop of orange vs clean gray
    labels = c("No", "Yes"),
    name = "Analyzed?"
  ) +
  
  # changing the labels of each course into their course names + course discipline
  scale_y_discrete(
    limits = c("F21_76247", "S22_82273" ,"F24_82270", "F24_82273", "F25_79211", 
               "F21_85221", "S25_84389", "S26_84389"),
    labels = c("F21 76-247 Shakespeare: Comedies & Romances 
               (Humanities)", 
               "S22 82-273 Japanese Culture and Society
               (Humanities)",
               "F24 82-270 Technology in Japanese Culture and Society
               (Humanities)",
               "F24 82-273 Japanese Culture and Society
               (Humanities)",
               "F25 79-211 Modern Southeast Asia
               (Humanities)",
               "F21 85-211 Principles of Child Development
               (Social Science)",
               "S25 84-389 Terrorism and Insurgency
               (Social Science)", 
               "S26 84-389 Terrorism and Insurgency
               (Social Science)") 
  ) +
  
  labs(title = "Type of Assignment Analyzed for Each Course", x = NULL, y = NULL) +
  
  # removes gray background
  theme_minimal()

```

## Creating Binary Grid Plot of the Assignment Time Given by Each Course ##

```{r}
# dataframe for setting binary grid plot
course_assignment_binary <- modified_df %>%
  # keep only one artifact from each course and their assignment time
  distinct(semester_courseNum, assignmentTime) %>% 
  # add a new variable that checks if there is an early and/or late assignment
  # assigned by a course
  mutate(Assigned = TRUE) %>% 
  # turns the missing values of assignment time into FALSE for the assigned variable
  complete(semester_courseNum, assignmentTime = c("Early", "Late"), fill = list(Assigned = FALSE))

ggplot(course_assignment_binary, aes(x = assignmentTime, y = semester_courseNum, fill = Assigned)) +
  # tile plot
  geom_tile(color = "black", lwd = 1) + 
  
  # color specification
  scale_fill_manual(
    values = c("TRUE" = "green", "FALSE" = "red"), # Pop of orange vs clean gray
    labels = c("No", "Yes"),
    name = "Analyzed?"
  ) +
  
  # changing the labels of each course into their course names + course discipline
  scale_y_discrete(
    limits = c("F21_76247", "S22_82273" ,"F24_82270", "F24_82273", "F25_79211", 
               "F21_85221", "S25_84389", "S26_84389"),
    labels = c("F21 76-247 Shakespeare: Comedies & Romances 
               (Humanities)", 
               "S22 82-273 Japanese Culture and Society
               (Humanities)",
               "F24 82-270 Technology in Japanese Culture and Society
               (Humanities)",
               "F24 82-273 Japanese Culture and Society
               (Humanities)",
               "F25 79-211 Modern Southeast Asia
               (Humanities)",
               "F21 85-211 Principles of Child Development
               (Social Science)",
               "S25 84-389 Terrorism and Insurgency
               (Social Science)", 
               "S26 84-389 Terrorism and Insurgency
               (Social Science)") 
  ) +
  
  labs(title = "Time of Assignment Analyzed for Each Course", x = NULL, y = NULL) +
  
  # removes gray background
  theme_minimal()

```

### Boxplot for the number of pages for each assignment type ###

```{r}
ggplot(modified_df, aes(x = assignmentType, y = numPages, fill = courseDiscipline)) +
  # boxplot
  geom_boxplot(color = "black", outlier.color = "red") +
  
  # ticks for the y-axis
  scale_y_continuous(breaks = seq(0, 26, by = 2)) +
  
  labs(title = "Number of Pages By Assignment Type",
       x = NULL,
       y = "Number of Pages") +
  theme_minimal() +
  
  theme(legend.position = "right") +
  
  # Legend Title and Description
  scale_fill_brewer(palette = "Pastel1", name = "Course Discipline", 
                    labels = c("Humanities (5 courses)", 
                               "Social Science (3 courses)"))
```

### Boxplot for the number of pages for each assignment time ###

```{r}
ggplot(modified_df, aes(x = assignmentTime, y = numPages, fill = courseDiscipline)) +
  # boxplot
  geom_boxplot(color = "black", outlier.color = "red") +
  
  # ticks for the y-axis
  scale_y_continuous(breaks = seq(0, 26, by = 2)) +
  
  labs(title = "Number of Pages By Assignment Time",
       x = NULL,
       y = "Number of Pages") +
  
  theme_minimal() +
  
  theme(legend.position = "right") +
  
  # Legend Titles and Description
  scale_fill_brewer(palette = "Pastel1", name = "Course Discipline", 
                    labels = c("Humanities (5 courses)", 
                               "Social Science (3 courses)"))
```

## Looking at the relationship between Assignment Type and CXT Ratings ## 
## for Each CXT Learning Outcome ##

```{r}
# Dataset with the mean rating, standard deviation of the rating, 
# and number of artifacts for each CXT learning outcome by Assignment Type 

# CXT 1 #
cxt1_mean <- modified_df %>% 
  # filtering out all missing values for NAs/ artifacts where CXT 1 wasn't coded
  filter(!is.na(cxt1)) %>% 
  # grouping by assignment type (main grouping) and course discipline (subgrouping)
  group_by(assignmentType, courseDiscipline) %>% 
  summarize(
    meanRating = mean(cxt1), # average CXT 1 rating
    se = sd(cxt1) / sqrt(n()), # standard deviation of CXT 1 rating
    count = n() # number of artifacts in each assignment type for each course discipline
  )

# CXT 2a # 
cxt2a_mean <- modified_df %>% 
  # filtering out all missing values for NAs/ artifacts where CXT 2a wasn't coded
  filter(!is.na(cxt2a)) %>% 
  # grouping by assignment type (main grouping) and course discipline (subgrouping)
  group_by(assignmentType, courseDiscipline) %>% 
  summarize(
    meanRating = mean(cxt2a), # average CXT 2a rating
    se = sd(cxt2a) / sqrt(n()), # standard deviation of CXT 2a rating
    count = n() # number of artifacts in each assignment type for each course discipline
  )

# CXT 2b #
cxt2b_mean <- modified_df %>%
  # filtering out all missing values for NAs/ artifacts where CXT 2b wasn't coded
  filter(!is.na(cxt2b)) %>% 
  # grouping by assignment type (main grouping) and course discipline (subgrouping)
  group_by(assignmentType, courseDiscipline) %>% 
  summarize(
    meanRating = mean(cxt2b), # average CXT 2b rating
    se = sd(cxt2b) / sqrt(n()), # standard deviation of CXT 2b rating
    count = n() # number of artifacts in each assignment type for each course discipline
  )

# CXT 3 #
cxt3_mean <- modified_df %>% 
  # filtering out all missing values for NAs/ artifacts where CXT 3 wasn't coded
  filter(!is.na(cxt3)) %>% 
  # grouping by assignment type (main grouping) and course discipline (subgrouping)
  group_by(assignmentType, courseDiscipline) %>% 
  summarize(
    meanRating = mean(cxt3), # average CXT 3 rating
    se = sd(cxt3) / sqrt(n()), # standard deviation of CXT 3 rating
    count = n() # number of artifacts in each assignment type for each course discipline
  )

# CXT 4a #
cxt4a_mean <- modified_df %>%
  # filtering out all missing values for NAs/ artifacts where CXT 4a wasn't coded
  filter(!is.na(cxt4a)) %>% 
  # grouping by assignment type (main grouping) and course discipline (subgrouping)
  group_by(assignmentType, courseDiscipline) %>% 
  summarize(
    meanRating = mean(cxt4a), # average CXT 4a rating
    se = sd(cxt4a) / sqrt(n()), # standard deviation of CXT 4a rating
    count = n() # number of artifacts in each assignment type for each course discipline
  )

# CXT 4b #
cxt4b_mean <- modified_df %>% 
  # filtering out all missing values for NAs/ artifacts where CXT 4b wasn't coded
  filter(!is.na(cxt4b)) %>% 
  # grouping by assignment type (main grouping) and course discipline (subgrouping)
  group_by(assignmentType, courseDiscipline) %>% 
  summarize(
    meanRating = mean(cxt4b), # average CXT 4b rating
    se = sd(cxt4b) / sqrt(n()), # standard deviation of CXT 4b rating
    count = n() # number of artifacts in each assignment type for each course discipline
  )
```


### Bar Graph of the Ratings for Each CXT Learning Outcome by Assignment Type ###

#### CXT1 ####

```{r}
ggplot(cxt1_mean, aes(x = assignmentType, y = meanRating, fill = courseDiscipline)) +
  # bar graph
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), color = "black", width = 0.7) +
  
  # 95% confidence intervals for each course discipline
  geom_errorbar(aes(ymin = meanRating - 2*se, ymax = meanRating + 2*se), position = position_dodge(width = 0.8), width = 0.2) +
  
  # adding the confidence interval range for CXT rating as a label
  geom_text(
    aes(label = paste0(round(meanRating, 2), " ± ", round(2 * se, 2)), 
        y = meanRating + 2 * se), 
    position = position_dodge(width = 0.8), 
    vjust = -0.8, size = 3.5
  ) +
  
  # adding the number of artifacts coded for CXT 1 in each course discipline 
  geom_text(
    aes(label = paste0("N = ", count), 
        y = meanRating / 2),
    position = position_dodge(width = 0.8), 
    vjust = -0.8
  ) +
  
  labs(title = "Average CXT1 Rating by Assignment Type",
       subtitle = "CXT1: Frame and reframe fundamental questions (who, what, where, when, why, and how) in order to interpret issues, objects, events, etc. ",
       x = NULL,
       y = "Rating (scale of 0-4)", 
       fill = "Course Discipline") +
  
  # removes gray background
  theme_minimal() +
  
  theme(legend.position = "right") +
  
  # Legend Titles and Description
  scale_fill_brewer(palette = "Pastel1", name = "Course Discipline", 
                    labels = c("Humanities (5 courses)", 
                               "Social Science (3 courses)")) + 
  
  ylim(0, 4)
  
```

#### CXT2a ####

```{r}
ggplot(cxt2a_mean, aes(x = assignmentType, y = meanRating, fill = courseDiscipline)) +
  # bar graph
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), color = "black", width = 0.7) +
  
  # 95% confidence intervals for each course discipline
  geom_errorbar(aes(ymin = meanRating - 2*se, ymax = meanRating + 2*se), position = position_dodge(width = 0.8), width = 0.2) +
  
  # adding the confidence interval range for CXT rating as a label
  geom_text(
    aes(label = paste0(round(meanRating, 2), " ± ", round(2 * se, 2)), 
        y = meanRating + 2 * se), 
    position = position_dodge(width = 0.8), 
    vjust = -0.8, size = 3.5
  ) +
  
  # adding the number of artifacts coded for CXT 2a in each course discipline
  geom_text(
    aes(label = paste0("N = ", count), 
        y = meanRating / 2),
    position = position_dodge(width = 0.8), 
    vjust = -0.8
  ) +
  
  labs(title = "Mean CXT2a Rating by Assignment Type",
       subtitle = "CXT2a: Select quality materials that enrich inquiry, such as archival records, media sources, literary texts, letters, journals, official documents, images, etc.",
       x = NULL,
       y = "Rating (scale of 0-4)", 
       fill = "Course Discipline") +
  
  # removes gray background
  theme_minimal() +
  
  theme(legend.position = "right") +
  
  # Legend Titles and Description
  scale_fill_brewer(palette = "Pastel1", name = "Course Discipline", 
                    labels = c("Humanities (5 courses)", 
                               "Social Science (3 courses)")) + 
  
  ylim(0, 4)
  
```

#### CXT2b ####

```{r}
ggplot(cxt2b_mean, aes(x = assignmentType, y = meanRating, fill = courseDiscipline)) +
  # bar graph
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), color = "black", width = 0.7) +
  
  # 95% confidence intervals for each course discipline
  geom_errorbar(aes(ymin = meanRating - 2*se, ymax = meanRating + 2*se), position = position_dodge(width = 0.8), width = 0.2) +
  
  # adding the confidence interval range for CXT rating as a label
  geom_text(
    aes(label = paste0(round(meanRating, 2), " ± ", round(2 * se, 2)), 
        y = meanRating + 2 * se), 
    position = position_dodge(width = 0.8), 
    vjust = -0.8, size = 3.5
  ) +
  
  # adding the number of artifacts coded for CXT 2b in each course discipline
  geom_text(
    aes(label = paste0("N = ", count), 
        y = meanRating / 2),
    position = position_dodge(width = 0.8), 
    vjust = -0.8
  ) +
  
  labs(title = "Mean CXT2b Rating by Assignment Type",
       subtitle = "CXT2b: Use and interpret evidence from source materials transparently and strategically to support major points.",
       x = NULL,
       y = "Rating (scale of 0-4)", 
       fill = "Course Discipline") +
  
  # removes gray background
  theme_minimal() +
  
  theme(legend.position = "right") +
  
  # Legend Titles and Description
  scale_fill_brewer(palette = "Pastel1", name = "Course Discipline", 
                    labels = c("Humanities (5 courses)", 
                               "Social Science (3 courses)")) + 
  
  ylim(0, 4)
```

#### CXT3 ####

```{r}
ggplot(cxt3_mean, aes(x = assignmentType, y = meanRating, fill = courseDiscipline)) +
  # bar graph
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), color = "black", width = 0.7) +
  
  # 95% confidence intervals for each course discipline
  geom_errorbar(aes(ymin = meanRating - 2*se, ymax = meanRating + 2*se), position = position_dodge(width = 0.8), width = 0.2) +
  
  # adding the confidence interval range for CXT rating as a label
  geom_text(
    aes(label = paste0(round(meanRating, 2), " ± ", round(2 * se, 2)), 
        y = meanRating + 2 * se), 
    position = position_dodge(width = 0.8), 
    vjust = -0.8, size = 3.5
  ) +
  
  # adding the number of artifacts coded for CXT 3 in each course discipline
  geom_text(
    aes(label = paste0("N = ", count), 
        y = meanRating / 2),
    position = position_dodge(width = 0.8), 
    vjust = -0.8
  ) +
  
  labs(title = "Mean CXT3 Rating by Assignment Type",
       subtitle = "CXT3: Analyze issues, objects, and events by interpreting these in relation to phenomena beyond the recent past (i.e. past twenty years).",
       x = NULL,
       y = "Rating (scale of 0-4)", 
       fill = "Course Discipline") +
  
  # removes gray background
  theme_minimal() +
  
  theme(legend.position = "right") +
  
  # Legend Titles and Description
  scale_fill_brewer(palette = "Pastel1", name = "Course Discipline", 
                    labels = c("Humanities (5 courses)", 
                               "Social Science (3 courses)")) + 
  
  ylim(0, 4)
```

#### CXT4a ####

```{r}
ggplot(cxt4a_mean, aes(x = assignmentType, y = meanRating, fill = courseDiscipline)) +
  # bar graph
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), color = "black", width = 0.7) +
  
  # 95% confidence intervals for each course discipline
  geom_errorbar(aes(ymin = meanRating - 2*se, ymax = meanRating + 2*se), position = position_dodge(width = 0.8), width = 0.2) +
  
  # adding the confidence interval range for CXT rating as a label
  geom_text(
    aes(label = paste0(round(meanRating, 2), " ± ", round(2 * se, 2)), 
        y = meanRating + 2 * se), 
    position = position_dodge(width = 0.8), 
    vjust = -0.8, size = 3.5
  ) +
  
  # adding the number of artifacts coded for CXT 4a in each course discipline
  geom_text(
    aes(label = paste0("N = ", count), 
        y = meanRating / 2),
    position = position_dodge(width = 0.8), 
    vjust = -0.8
  ) +
  
  labs(title = "Mean CXT4a Rating by Assignment Type",
       subtitle = "CXT4a: Consider how ways of thinking developed over time.",
       x = NULL,
       y = "Rating (scale of 0-4)", 
       fill = "Course Discipline") +
  
  # removes gray background
  theme_minimal() +
  
  theme(legend.position = "right") +
  
  # Legend Titles and Description
  scale_fill_brewer(palette = "Pastel1", name = "Course Discipline", 
                    labels = c("Humanities (5 courses)", 
                               "Social Science (3 courses)")) + 
  
  ylim(0, 4)
```

#### CXT4b ####

```{r}
ggplot(cxt4b_mean, aes(x = assignmentType, y = meanRating, fill = courseDiscipline)) +
  # bar graph
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), color = "black", width = 0.7) +
  
  # 95% confidence intervals for each course discipline
  geom_errorbar(aes(ymin = meanRating - 2*se, ymax = meanRating + 2*se), position = position_dodge(width = 0.8), width = 0.2) +
  
  # adding the confidence interval range for CXT rating as a label
  geom_text(
    aes(label = paste0(round(meanRating, 2), " ± ", round(2 * se, 2)), 
        y = meanRating + 2 * se), 
    position = position_dodge(width = 0.8), 
    vjust = -0.8, size = 3.5
  ) +
  
  # adding the number of artifacts coded for CXT 4a in each course discipline
  geom_text(
    aes(label = paste0("N = ", count), 
        y = meanRating / 2),
    position = position_dodge(width = 0.8), 
    vjust = -0.8
  ) +
  
  labs(title = "Mean CXT4b Rating by Assignment Type",
       subtitle = "CXT4b: The student articulates their own way of thinking in the context of normative thinking traditions.",
       x = NULL,
       y = "Rating (scale of 0-4)", 
       fill = "Course Discipline") +
  
  # removes gray background
  theme_minimal() +
  
  theme(legend.position = "right") +
  
  # Legend Titles and Description
  scale_fill_brewer(palette = "Pastel1", name = "Course Discipline", 
                    labels = c("Humanities (5 courses)", 
                               "Social Science (3 courses)")) + 
  
  ylim(0, 4)
```

## Looking at the Relationship between Early vs. Late Assignment for Each CXT Learning Outcome ##

```{r}
# Dataset with the mean rating, standard deviation of the rating, and 
# number of artifacts for each CXT learning outcome by Assignment Time

# CXT 1 #
cxt1_early_late <- modified_df %>% 
  # filtering out all missing values for NAs/ artifacts where CXT 1 wasn't coded
  filter(!is.na(cxt1)) %>% 
  # grouping by assignment time (main grouping) and course discipline (subgrouping)
  group_by(assignmentTime, courseDiscipline) %>% 
  summarize(
    meanRating = mean(cxt1), # average CXT 1 rating
    se = sd(cxt1) / sqrt(n()), # standard deviation of CXT 1 rating
    count = n() # number of artifacts in each assignment time for each course discipline
  )

# CXT 2a # 
cxt2a_early_late <- modified_df %>% 
  # filtering out all missing values for NAs/ artifacts where CXT 2a wasn't coded
  filter(!is.na(cxt2a)) %>% 
  # grouping by assignment time (main grouping) and course discipline (subgrouping)
  group_by(assignmentTime, courseDiscipline) %>% 
  summarize(
    meanRating = mean(cxt2a), # average CXT 2a rating
    se = sd(cxt2a) / sqrt(n()), # standard deviation of CXT 2a rating
    count = n() # number of artifacts in each assignment time for each course discipline
  )

# CXT 2b #
cxt2b_mean <- modified_df %>%
  # filtering out all missing values for NAs/ artifacts where CXT 2b wasn't coded
  filter(!is.na(cxt2b)) %>% 
  # grouping by assignment time (main grouping) and course discipline (subgrouping)
  group_by(assignmentTime, courseDiscipline) %>% 
  summarize(
    meanRating = mean(cxt2b), # average CXT 2b rating
    se = sd(cxt2b) / sqrt(n()), # standard deviation of CXT 2b rating
    count = n() # number of artifacts in each assignment time for each course discipline
  )

# CXT 3 #
cxt3_early_late <- modified_df %>% 
  # filtering out all missing values for NAs/ artifacts where CXT 3 wasn't coded
  filter(!is.na(cxt3)) %>% 
  # grouping by assignment time (main grouping) and course discipline (subgrouping)
  group_by(assignmentTime, courseDiscipline) %>% 
  summarize(
    meanRating = mean(cxt3), # average CXT 3 rating
    se = sd(cxt3) / sqrt(n()), # standard deviation of CXT 3 rating
    count = n() # number of artifacts in each assignment time for each course discipline
  )

# CXT 4a #
cxt4a_early_late <- modified_df %>%
  # filtering out all missing values for NAs/ artifacts where CXT 4a wasn't coded
  filter(!is.na(cxt4a)) %>% 
  # grouping by assignment time (main grouping) and course discipline (subgrouping)
  group_by(assignmentTime, courseDiscipline) %>% 
  summarize(
    meanRating = mean(cxt4a), # average CXT 4a rating
    se = sd(cxt4a) / sqrt(n()), # standard deviation of CXT 4a rating
    count = n() # number of artifacts in each assignment time for each course discipline
  )

# CXT 4b #
cxt4b_early_late <- modified_df %>% 
  # filtering out all missing values for NAs/ artifacts where CXT 4b wasn't coded
  filter(!is.na(cxt4b)) %>% 
  # grouping by assignment time (main grouping) and course discipline (subgrouping)
  group_by(assignmentTime, courseDiscipline) %>% 
  summarize(
    meanRating = mean(cxt4b), # average CXT 4b rating
    se = sd(cxt4b) / sqrt(n()), # standard deviation of CXT 4b rating
    count = n() # number of artifacts in each assignment time for each course discipline
  )

```

### Bar Graph of the Ratings for Each CXT Learning Outcome by Assignment Time ###

#### CXT 1 ####

```{r}
ggplot(cxt1_early_late, aes(x = assignmentTime, y = meanRating, fill = courseDiscipline)) +
  # bar graph
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), color = "black", width = 0.7) +
  
  # 95% confidence intervals for each course discipline
  geom_errorbar(aes(ymin = meanRating - 2*se, ymax = meanRating + 2*se), position = position_dodge(width = 0.8), width = 0.2) +
  
  # adding the confidence interval range for CXT rating as a label
  geom_text(
    aes(label = paste0(round(meanRating, 2), " ± ", round(2 * se, 2)), 
        y = meanRating + 2 * se), 
    position = position_dodge(width = 0.8), 
    vjust = -0.8, size = 3.5
  ) +
  
  # adding the number of artifacts coded for CXT 1 in each course discipline
  geom_text(
    aes(label = paste0("N = ", count), 
        y = meanRating / 2),
    position = position_dodge(width = 0.8), 
    vjust = -0.8
  ) +
  
  labs(title = "Mean CXT1 Rating by Assignment Time",
       subtitle = "CXT1: Frame and reframe fundamental questions (who, what, where, when, why, and how) in order to interpret issues, objects, events, etc.",
       x = NULL,
       y = "Rating (scale of 0-4)", 
       fill = "Course Discipline") +
  
  # removes gray background
  theme_minimal() +
  
  theme(legend.position = "right") +
  
  # Legend Titles and Description
  scale_fill_brewer(palette = "Pastel1", name = "Course Discipline", 
                    labels = c("Humanities (5 courses)", 
                               "Social Science (3 courses)")) + 
  
  ylim(0, 4)
  
```


```{r}
ggplot(cxt2a_early_late, aes(x = assignmentTime, y = meanRating, fill = courseDiscipline)) +
  # bar graph
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), color = "black", width = 0.7) +
  
  # 95% confidence intervals for each course discipline
  geom_errorbar(aes(ymin = meanRating - 2*se, ymax = meanRating + 2*se), position = position_dodge(width = 0.8), width = 0.2) +
  
  # adding the confidence interval range for CXT rating as a label
  geom_text(
    aes(label = paste0(round(meanRating, 2), " ± ", round(2 * se, 2)), 
        y = meanRating + 2 * se), 
    position = position_dodge(width = 0.8), 
    vjust = -0.8, size = 3.5
  ) +
  
   # adding the number of artifacts coded for CXT 2a in each course discipline
  geom_text(
    aes(label = paste0("N = ", count), 
        y = meanRating / 2),
    position = position_dodge(width = 0.8), 
    vjust = -0.8
  ) +
  
  labs(title = "Mean CXT2a Rating by Assignment Time",
       subtitle = "CXT2a: Select quality materials that enrich inquiry, such as archival records, media sources, literary texts, letters, journals, official documents, images, etc.",
       x = NULL,
       y = "Rating (scale of 0-4)", 
       fill = "Course Discipline") +
  
  # removes gray background
  theme_minimal() +
  
  theme(legend.position = "right") +
  
  # Legend Titles and Description
  scale_fill_brewer(palette = "Pastel1", name = "Course Discipline", 
                    labels = c("Humanities (5 courses)", 
                               "Social Science (3 courses)")) + 
  
  ylim(0, 4)
  
```


```{r}
ggplot(cxt2b_early_late, aes(x = assignmentTime, y = meanRating, fill = courseDiscipline)) +
  # bar graph
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), color = "black", width = 0.7) +
  
  # 95% confidence intervals for each course discipline
  geom_errorbar(aes(ymin = meanRating - 2*se, ymax = meanRating + 2*se), position = position_dodge(width = 0.8), width = 0.2) +
  
  # adding the confidence interval range for CXT rating as a label
  geom_text(
    aes(label = paste0(round(meanRating, 2), " ± ", round(2 * se, 2)), 
        y = meanRating + 2 * se), 
    position = position_dodge(width = 0.8), 
    vjust = -0.8, size = 3.5
  ) +
  
  # adding the number of artifacts coded for CXT 2b in each course discipline
  geom_text(
    aes(label = paste0("N = ", count), 
        y = meanRating / 2),
    position = position_dodge(width = 0.8), 
    vjust = -0.8
  ) +
  
  labs(title = "Average CXT2b Rating by Assignment Time",
       subtitle = "CXT2b: Use and interpret evidence from source materials transparently and strategically to support major points.",
       x = NULL,
       y = "Rating (scale of 0-4)", 
       fill = "Course Discipline") +
  
  # removes gray background
  theme_minimal() +
  
  theme(legend.position = "right") +
  
  # Legend Titles and Description
  scale_fill_brewer(palette = "Pastel1", name = "Course Discipline", 
                    labels = c("Humanities (5 courses)", 
                               "Social Science (3 courses)")) + 
  
  ylim(0, 4)
  
```


```{r}
ggplot(cxt3_early_late, aes(x = assignmentTime, y = meanRating, fill = courseDiscipline)) +
  # bar graph
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), color = "black", width = 0.7) +
  
  
  # 95% confidence intervals for each course discipline
  geom_errorbar(aes(ymin = meanRating - 2*se, ymax = meanRating + 2*se), position = position_dodge(width = 0.8), width = 0.2) +
  
  # adding the confidence interval range for CXT rating as a label
  geom_text(
    aes(label = paste0(round(meanRating, 2), " ± ", round(2 * se, 2)), 
        y = meanRating + 2 * se), 
    position = position_dodge(width = 0.8), 
    vjust = -0.8, size = 3.5
  ) +
  
  # adding the number of artifacts coded for CXT 3 in each course discipline
  geom_text(
    aes(label = paste0("N = ", count), 
        y = meanRating / 2),
    position = position_dodge(width = 0.8), 
    vjust = -0.8
  ) +
  
  labs(title = "Mean CXT3 Rating by Assignment Time",
       subtitle = "CXT3: Analyze issues, objects, and events by interpreting these in relation to phenomena beyond the recent past (i.e. past twenty years)",
       x = NULL,
       y = "Rating (scale of 0-4)", 
       fill = "Course Discipline") +
  
  # removes gray background
  theme_minimal() +
  
  theme(legend.position = "right") +
  
  # Legend Titles and Description
  scale_fill_brewer(palette = "Pastel1", name = "Course Discipline", 
                    labels = c("Humanities (5 courses)", 
                               "Social Science (3 courses)")) + 
  
  ylim(0, 4)
```


```{r}
ggplot(cxt4a_early_late, aes(x = assignmentTime, y = meanRating, fill = courseDiscipline)) +
  # bar graph
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), color = "black", width = 0.7) +
  
  # 95% confidence intervals for each course discipline
  geom_errorbar(aes(ymin = meanRating - 2*se, ymax = meanRating + 2*se), position = position_dodge(width = 0.8), width = 0.2) +
  
  # adding the confidence interval range for CXT rating as a label
  geom_text(
    aes(label = paste0(round(meanRating, 2), " ± ", round(2 * se, 2)), 
        y = meanRating + 2 * se), 
    position = position_dodge(width = 0.8), 
    vjust = -0.8, size = 3.5
  ) +
  
  # adding the number of artifacts coded for CXT 4a in each course discipline
  geom_text(
    aes(label = paste0("N = ", count), 
        y = meanRating / 2),
    position = position_dodge(width = 0.8), 
    vjust = -0.8
  ) +
  
  labs(title = "Mean CXT4a Rating by Assignment Time",
       subtitle = "CXT4a: Consider how ways of thinking developed over time.",
       x = NULL,
       y = "Rating (scale of 0-4)", 
       fill = "Course Discipline") +
  
  # removes gray background
  theme_minimal() +
  
  theme(legend.position = "right") +
  
  # Legend Titles and Description
  scale_fill_brewer(palette = "Pastel1", name = "Course Discipline", 
                    labels = c("Humanities (5 courses)", 
                               "Social Science (3 courses)")) + 
  
  ylim(0, 4)
  
```


```{r}
ggplot(cxt4b_early_late, aes(x = assignmentTime, y = meanRating, fill = courseDiscipline)) +
  # bar graph
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), color = "black", width = 0.7) +
  
  # 95% confidence intervals for each course discipline
  geom_errorbar(aes(ymin = meanRating - 2*se, ymax = meanRating + 2*se), position = position_dodge(width = 0.8), width = 0.2) +
  
  # adding the confidence interval range for CXT rating as a label
  geom_text(
    aes(label = paste0(round(meanRating, 2), " ± ", round(2 * se, 2)), 
        y = meanRating + 2 * se), 
    position = position_dodge(width = 0.8), 
    vjust = -0.8, size = 3.5
  ) +
  
  # adding the number of artifacts coded for CXT 4b in each course discipline
  geom_text(
    aes(label = paste0("N = ", count), 
        y = meanRating / 2),
    position = position_dodge(width = 0.8), 
    vjust = -0.8
  ) +
  
  labs(title = "Mean CXT4b Rating by Assignment Time",
       subtitle = "CXT4b: The student articulates their own way of thinking in the context of normative thinking traditions",
       x = NULL,
       y = "Rating (scale of 0-4)", 
       fill = "Course Discipline") +
  
  # removes gray background
  theme_minimal() +
  
  theme(legend.position = "right") +
  
  # Legend Titles and Description
  scale_fill_brewer(palette = "Pastel1", name = "Course Discipline", 
                    labels = c("Humanities (5 courses)", 
                               "Social Science (3 courses)")) + 
  
  ylim(0, 4)
  
```
## Checking Correlation between Assignment Type and Assignment Time ##
## using Chi-Square Test ## 

```{r}
print(chisq.test(table(modified_df$assignmentType, modified_df$assignmentTime)))
```
## Multiple Linear Regression Models for Each CXT Learning Outcome ##

```{r}

# CXT 1 = β0 + β1 * (Number of Artifact Pages) + β2 * (0 for Humanities, 1 for Social Science) + 
# β3 * (0 for early, 1 for late) + β4 * (0 for 1 type of assignment chosen, 1 for more than 1) + 
# β5 * (0 for Humanities, 1 for Social Science) * (0 for early, 1 for late)

cxt1_linear <- lm(cxt1 ~ numPages + courseDiscipline + assignmentTime + courseDiscipline:assignmentTime + IsVaried, 
                  data = modified_df)


# prints model diagnostics
summary(cxt1_linear)
```

```{r}

# CXT 2a = β0 + β1 * (Number of Artifact Pages) + β2 * (0 for Humanities, 1 for Social Science) + 
# β3 * (0 for early, 1 for late) + β4 * (0 for 1 type of assignment chosen, 1 for more than 1)

cxt2a_linear <- lm(cxt2a ~ numPages + courseDiscipline + assignmentTime + IsVaried, 
                  data = modified_df)

# prints model diagnostics
summary(cxt2a_linear)
```

```{r}

# CXT 2b = β0 + β1 * (Number of Artifact Pages) + β2 * (0 for Humanities, 1 for Social Science) + 
# β3 * (0 for early, 1 for late) + β4 * (0 for 1 type of assignment chosen, 1 for more than 1)

cxt2b_linear <- lm(cxt2b ~ numPages + courseDiscipline + assignmentTime + IsVaried, 
                  data = modified_df)

# prints model diagnostics
summary(cxt2b_linear)
```

```{r}

# CXT 3 = β0 + β1 * (Number of Artifact Pages) + β2 * (0 for Humanities, 1 for Social Science) + 
# β3 * (0 for early, 1 for late) + β4 * (0 for 1 type of assignment chosen, 1 for more than 1) + 
# β5 * (0 for Humanities, 1 for Social Science) * (0 for early, 1 for late)

cxt3_linear <- lm(cxt3 ~ numPages + courseDiscipline + assignmentTime + courseDiscipline:assignmentTime + IsVaried, 
                  data = modified_df)

# prints model diagnostics
summary(cxt3_linear)
```

```{r}

# CXT 4a = β0 + β1 * (Number of Artifact Pages) + β2 * (0 for Humanities, 1 for Social Science) + 
# β3 * (0 for early, 1 for late) + β4 * (0 for 1 type of assignment chosen, 1 for more than 1) + 
# β5 * (0 for Humanities, 1 for Social Science) * (0 for early, 1 for late)

cxt4a_linear <- lm(cxt4a ~ numPages + courseDiscipline + assignmentTime + courseDiscipline:assignmentTime + IsVaried, 
                  data = modified_df)

# prints model diagnostics
summary(cxt4a_linear)
```

```{r}

# CXT 4b = β0 + β1 * (Number of Artifact Pages) + β2 * (0 for Humanities, 1 for Social Science) + 
# β3 * (0 for early, 1 for late) + β4 * (0 for 1 type of assignment chosen, 1 for more than 1) 

cxt4b_linear <- lm(cxt4b ~ numPages + courseDiscipline + assignmentTime + IsVaried, 
                  data = modified_df)

# prints model diagnostics
summary(cxt4b_linear)
```

## Spring 2026 84-389 Terrorism and Insurgency: Early vs. Late ##
## (with Same Type of Assignment for both assignments) ###

```{r}
# Running the Kruskal-Wallis Test on Each CXT Learning Outcome Coded for the Course Artifacts 

# print the test results for CXT 1
print(kruskal.test(cxt1 ~ assignmentTime, data = S26_84389))

# print the test results for CXT 3
print(kruskal.test(cxt3 ~ assignmentTime, data = S26_84389))

# print the test results for CXT 4a
print(kruskal.test(cxt4a ~ assignmentTime, data = S26_84389))
```
### Checking for Difference in Rating Between Early and Late ###

```{r}
# prints the model diagnostics of a simple linear regression model 

# CXT 1 = β0 + β1 * (0 for early, 1 for late)

summary(lm(cxt1 ~ assignmentTime, data = S26_84389))
```















