---
title: "Sura Project 2 - Grace Xu"
output:
  html_document:
    df_print: paged
---
#set up and merge data
```{r}
response_data <- read.csv(
  "~/Desktop/CXT SURA Data Entry (Responses) - Form Responses 1.csv",
  header = TRUE
)
names(response_data)

demographics_data <- read.csv(
  "~/Desktop/demographics_data.csv",
  header = TRUE
)

names(demographics_data)

merged_data <- merge(
  response_data,
  demographics_data,
  by.x = "DCID..EX..DC1233.or.DCF2456.",
  by.y = "DCID2",
  all.x = TRUE
)

dim(merged_data)
names(merged_data)
head(merged_data[, c(
  "DCID..EX..DC1233.or.DCF2456.",
  "SEX",
  "FIRST.GEN"
)])

merged_data$DomesticStatus <- ifelse(
  merged_data$CITIZENSHIP %in% c("U", "P"),
  "Domestic",
  "International"
)
```

#merge data and do t-tests against cxts and gender
```{r}

merged_data$FIRST_GEN <- merged_data$FIRST.GEN

merged_data$DomesticStatus <- ifelse(
  merged_data$CITIZENSHIP %in% c("U", "P"),
  "Domestic",
  "International"
)

gender_data <- subset(
  merged_data,
  SEX %in% c("F", "M")
)

t.test(CXT1 ~ SEX, data = gender_data)
t.test(CXT2a ~ SEX, data = gender_data)
t.test(CXT2b ~ SEX, data = gender_data)
t.test(CXT3 ~ SEX, data = gender_data)
t.test(CXT4a ~ SEX, data = gender_data)
t.test(CXT4b ~ SEX, data = gender_data)

```

# t-test against cxts and first generation status
```{r}
firstgen_data <- subset(
  merged_data,
  FIRST_GEN %in% c("Y", "N")
)

table(firstgen_data$FIRST_GEN)

t.test(CXT1 ~ FIRST_GEN, data = firstgen_data)
t.test(CXT2a ~ FIRST_GEN, data = firstgen_data)
t.test(CXT2b ~ FIRST_GEN, data = firstgen_data)
t.test(CXT3 ~ FIRST_GEN, data = firstgen_data)
t.test(CXT4a ~ FIRST_GEN, data = firstgen_data)
t.test(CXT4b ~ FIRST_GEN, data = firstgen_data)
```

#regression for high school gpa
```{r}

lm(CXT1 ~ HS.QPA, data = merged_data)
summary(lm(CXT1 ~ HS.QPA, data = merged_data))

summary(lm(CXT2a ~ HS.QPA, data = merged_data))
summary(lm(CXT2b ~ HS.QPA, data = merged_data))
summary(lm(CXT3 ~ HS.QPA, data = merged_data))
summary(lm(CXT4a ~ HS.QPA, data = merged_data))
summary(lm(CXT4b ~ HS.QPA, data = merged_data))
```

#anova for race
```{r}
table(merged_data$RACE.S.)
summary(aov(CXT1 ~ RACE.S., data = merged_data))
summary(aov(CXT2a ~ RACE.S., data = merged_data))
summary(aov(CXT2b ~ RACE.S., data = merged_data))
summary(aov(CXT3 ~ RACE.S., data = merged_data))
summary(aov(CXT4a ~ RACE.S., data = merged_data))
summary(aov(CXT4b ~ RACE.S., data = merged_data))

TukeyHSD(aov(CXT1 ~ RACE.S., data = merged_data))

TukeyHSD(aov(CXT3 ~ RACE.S., data = merged_data))
```

#multiple regression (include all demographic variables except high school gpa)
```{r}
merged_data$SEX <- factor(merged_data$SEX)
merged_data$FIRST_GEN <- factor(merged_data$FIRST_GEN)
merged_data$DomesticStatus <- factor(merged_data$DomesticStatus)
merged_data$RACE.S. <- factor(merged_data$RACE.S.)


merged_data$SEX[merged_data$SEX == ""] <- NA
merged_data$FIRST_GEN[merged_data$FIRST_GEN == ""] <- NA
merged_data$RACE.S.[merged_data$RACE.S. == ""] <- NA

merged_data$SEX <- factor(merged_data$SEX)
merged_data$FIRST_GEN <- factor(merged_data$FIRST_GEN)
merged_data$RACE.S. <- factor(merged_data$RACE.S.)

model_CXT1 <- lm(
  CXT1 ~ SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)
summary(model_CXT1)

model_CXT2a <- lm(
  CXT2a ~ SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)
summary(model_CXT2a)

model_CXT2b <- lm(
  CXT2b ~ SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)
summary(model_CXT2b)

model_CXT3 <- lm(
  CXT3 ~ SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)
summary(model_CXT3)

model_CXT4a <- lm(
  CXT4a ~ SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)
summary(model_CXT4a)

model_CXT4b <- lm(
  CXT4b ~ SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)
summary(model_CXT4b)

levels(merged_data$RACE.S.)

```

#multiple regression with all demographic variables
```{r}
model_CXT1 <- lm(
  CXT1 ~ HS.QPA + SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)
summary(model_CXT1)

model_CXT2a <- lm(
  CXT2a ~ HS.QPA + SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)
summary(model_CXT2a)

model_CXT2b <- lm(
  CXT2b ~ HS.QPA + SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)
summary(model_CXT2b)

model_CXT3 <- lm(
  CXT3 ~ HS.QPA + SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)
summary(model_CXT3)

model_CXT4a <- lm(
  CXT4a ~ HS.QPA + SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)
summary(model_CXT4a)

model_CXT4b <- lm(
  CXT4b ~ HS.QPA + SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)
summary(model_CXT4b)
```

#standardized regression coefficients (β) - to see which variable has strongest influence on each cxts
```{r}

# Load package
library(lm.beta)

# CXT1
model_CXT1 <- lm(
  CXT1 ~ HS.QPA + SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)

summary(lm.beta(model_CXT1))

# CXT2a
model_CXT2a <- lm(
  CXT2a ~ HS.QPA + SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)

summary(lm.beta(model_CXT2a))

# CXT2b
model_CXT2b <- lm(
  CXT2b ~ HS.QPA + SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)

summary(lm.beta(model_CXT2b))

# CXT3
model_CXT3 <- lm(
  CXT3 ~ HS.QPA + SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)

summary(lm.beta(model_CXT3))

# CXT4a
model_CXT4a <- lm(
  CXT4a ~ HS.QPA + SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)

summary(lm.beta(model_CXT4a))

# CXT4b
model_CXT4b <- lm(
  CXT4b ~ HS.QPA + SEX + FIRST_GEN + DomesticStatus + RACE.S.,
  data = merged_data
)

summary(lm.beta(model_CXT4b))

models <- list(
  CXT1  = model_CXT1,
  CXT2a = model_CXT2a,
  CXT2b = model_CXT2b,
  CXT3  = model_CXT3,
  CXT4a = model_CXT4a,
  CXT4b = model_CXT4b
)

for(i in names(models)) {

  beta <- lm.beta(models[[i]])$standardized.coefficients

  beta <- beta[names(beta) != "(Intercept)"]

  cat("\n", i, "\n")
  print(sort(abs(beta), decreasing = TRUE))
}
```

#calculate average scores for each cxts
```{r}
library(tidyverse)

cxt_means <- data.frame(
  CXT = c("CXT1","CXT2a","CXT2b","CXT3","CXT4a","CXT4b"),
  Mean = c(
    mean(merged_data$CXT1, na.rm = TRUE),
    mean(merged_data$CXT2a, na.rm = TRUE),
    mean(merged_data$CXT2b, na.rm = TRUE),
    mean(merged_data$CXT3, na.rm = TRUE),
    mean(merged_data$CXT4a, na.rm = TRUE),
    mean(merged_data$CXT4b, na.rm = TRUE)
  )
)

ggplot(cxt_means,
       aes(x = reorder(CXT, Mean),
           y = Mean,
           fill = Mean)) +
  geom_col(width = .7) +
  geom_text(aes(label = round(Mean,2)),
            hjust = -0.2,
            size = 5) +
  coord_flip() +
  theme_minimal(base_size = 16) +
  labs(
    title = "Average Scores Across CXT Dimensions",
    x = "",
    y = "Mean Score"
  ) +
  theme(legend.position = "none")
```

#heat map
```{r}
library(tidyverse)

beta_data <- data.frame(
  Variable = c("HS.QPA","Male","First Gen","International"),
  CXT1  = c(0.182,0.099,0.136,-0.135),
  CXT2a = c(0.078,0.276,0.257,0.056),
  CXT2b = c(0.059,0.243,0.113,0.232),
  CXT3  = c(-0.010,0.251,0.045,0.054),
  CXT4a = c(0.225,-0.075,0.224,0.122),
  CXT4b = c(0.001,-0.054,0.169,0.256)
)

beta_long <- pivot_longer(
  beta_data,
  cols = -Variable,
  names_to = "CXT",
  values_to = "Beta"
)

ggplot(beta_long,
       aes(CXT, Variable, fill = Beta)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(Beta,2)),
            size = 5) +
  scale_fill_gradient2(
    low = "#2166ac",
    mid = "white",
    high = "#b2182b",
    midpoint = 0
  ) +
  theme_minimal(base_size = 16) +
  labs(
    title = "Demographic Influences Across CXT Dimensions",
    fill = "β"
  )
```

#Calculate the average score for each CXT dimension
#separately for first-generation and non-first-generation students
```{r}
library(tidyverse)

fg_data <- merged_data %>%
  group_by(FIRST_GEN) %>%
  summarise(
    CXT1 = mean(CXT1, na.rm=TRUE),
    CXT2a = mean(CXT2a, na.rm=TRUE),
    CXT2b = mean(CXT2b, na.rm=TRUE),
    CXT3 = mean(CXT3, na.rm=TRUE),
    CXT4a = mean(CXT4a, na.rm=TRUE),
    CXT4b = mean(CXT4b, na.rm=TRUE)
  ) %>%
  pivot_longer(
    -FIRST_GEN,
    names_to="CXT",
    values_to="Score"
  )

ggplot(fg_data,
       aes(CXT, Score,
           fill=FIRST_GEN)) +
  geom_col(position="dodge") +
  theme_minimal(base_size=16) +
  labs(
    title="First-Generation vs Non-First-Generation Students"
  )
```

#Create a summary table showing the strongest significantdemographic predictor for each CXT dimension based on
#the multiple regression results
```{r}
sig <- data.frame(
  CXT = c("CXT1","CXT2a","CXT2b","CXT3","CXT4a","CXT4b"),
  Strongest = c(
    "Race(HW)",
    "Sex",
    "Sex",
    "Race(W)",
    "HS.QPA",
    "Citizenship"
  )
)

ggplot(sig,
       aes(x=CXT,
           y=Strongest,
           fill=Strongest)) +
  geom_tile(color="white") +
  geom_text(aes(label=Strongest),
            size=5) +
  theme_minimal(base_size=16) +
  theme(
    legend.position="none"
  ) +
  labs(
    title="Most Influential Demographic Factor for Each CXT Dimension"
  )
```

#Create scatterplots showing the relationship between high school GPA and each CXT dimension.
```{r}

library(tidyverse)

cxt_long <- merged_data %>%
  pivot_longer(
    cols = c(CXT1, CXT2a, CXT2b, CXT3, CXT4a, CXT4b),
    names_to = "CXT",
    values_to = "Score"
  )

ggplot(cxt_long,
       aes(x = HS.QPA, y = Score)) +
  geom_point(alpha = .5) +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~CXT) +
  theme_minimal(base_size = 14) +
  labs(
    title = "Relationship Between High School GPA and CXT Dimensions",
    x = "High School GPA",
    y = "CXT Score"
  )


```

#box plot
```{r}
#Compare CXT3 scores between male and female students
boxplot(CXT3 ~ SEX,
        data = merged_data,
        main = "CXT3 by Gender",
        xlab = "Gender",
        ylab = "CXT3 Score")

#Compare CXT4b scores between domestic and international students
boxplot(CXT4b ~ DomesticStatus,
        data = merged_data,
        main = "CXT4b by Citizenship",
        xlab = "Citizenship Status",
        ylab = "CXT4b Score")

#Compare CXT2a scores between first-generation and non-first-generation students
boxplot(CXT2a ~ FIRST_GEN,
        data = merged_data,
        main = "CXT2a by First-Generation Status",
        xlab = "First Generation",
        ylab = "CXT2a Score")

#Examine the relationship between high school GPA and CXT4a scores
plot(merged_data$HS.QPA,
     merged_data$CXT4a,
     main = "HS GPA vs CXT4a",
     xlab = "High School GPA",
     ylab = "CXT4a Score")

abline(lm(CXT4a ~ HS.QPA, data = merged_data),
       col = "red",
       lwd = 2)

#Compare CXT3 scores across racial groups
boxplot(CXT3 ~ RACE.S.,
        data = merged_data,
        main = "CXT3 by Race",
        xlab = "Race",
        ylab = "CXT3 Score")
```